Additional analysis

### 2020-11-17 README.Rmd
Move badges up a little
Add links to data and notebook
Add NVSQ DOI

> `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming).

@@

> `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming).

>>>>

[![NVSQ DOI](https://img.shields.io/badge/NVSQ%20DOI-10.1177%2F0899764020971045-brightgreen)](https://doi.org/10.1177/0899764020971045) [![OSF DOI](https://img.shields.io/badge/OSF-10.17605%2FOSF.IO%2FFG53W-blue)](https://dx.doi.org/10.17605/OSF.IO/FG53W) [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.4058987.svg)](https://doi.org/10.5281/zenodo.4058987)

> `r Authors`. `r Year`. ["`r Title`,"](https://doi.org/10.1177/0899764020971045) *Nonprofit and Voluntary Sector Quarterly* (forthcoming), doi: [`10.1177/0899764020971045`](https://doi.org/10.1177/0899764020971045).

**All this project's materials are free and open:**

- [Download the data](#data)
- [See the analysis notebook website](https://stats.andrewheiss.com/ngo-crackdowns-philanthropy/)

![Preregistered](img/preregistered_large_color.png) &emsp; ![Open data](img/data_large_color.png) &emsp; ![Open](img/materials_large_color.png)

@@

> `r Authors`. `r Year`. "`r Title`," *Nonprofit and Voluntary Sector Quarterly* (forthcoming), doi: [`10.1177/0899764020971045`](https://doi.org/10.1177/0899764020971045).
